\bf\mftitle

### 2011-03-02 doc/jInfer/xsdimport/xsdimport.tex
last minute corrections

\subsection{Naming convention}
Note that there are several types of entities called `element' in the context of the described modules.
To avoid ambiguity, in this document we shall use notation \code{DOM.Element} 
for instances of \code{org.w3c.dom.Element} and notation \code{Element} 
for instances of\code{cz.cuni.mff.ksi.jinfer.base.objects.nodes.Element}.

@@

\begin{description}
	\item[CreateSentinel()] Creates an instance of \code{Element} class, which is always a leaf in the rule-tree. This is useful when there are cyclic definitions in an input Schema document, or an \code{Element} with this name was defined previously and it is unnecessary to build a rule subtree for it again (it is a reference in this case). More information about sentinels can be found in \cite[section 3.2]{archdoc}, or \cite[section 4]{twostepdoc}.
	\item[FinalizeElement()] Checks if \code{Element} is properly defined. Redefine it to \code{LAMBDA} when it was empty, or to token if it only contained a simple data type. This method allows for built-in data types of tags to be retained for export.
\end{description}

@@

Sax handler implements methods in response to the events generated by the underlying SAX parser API.
Similar to its counterpart, \code{DOMHandler}, this class holds most on the logic for importing a Schema.
It works by keeping current tree branch, which is being parsed, on a stack. Adding current node to the parent on top of the stack as current tag finishes.

\section{Data Flow}
Parsing of XSD begins when \code{IGGeneratorImpl} calls \code{XSDProcessor} with an input file.
The overall data flow while parsing a Schema document is simple, it can be summarized into following steps.
\begin{enumerate}
	\item \code{XSDProcessor} finds out the selected \code{XSDParser} from available service providers. This also indicates which module will be handling the actual parsing.
	\item \code{XSDProcessor} passes the input document to a selected module by calling \code{parse()} method on the selected \code{XSDParser}.
	\item Depending on the module, the corresponding API is used to extract IG rules from the input document.
	\item List of rules that were extracted from the document are returned to \code{XSDProcessor}.
	\item If no errors occured during this process, list of extracted rules is returned to \code{IGGeneratorImpl} for expansion. Otherwise, depending on the \emph{Stop on error} setting, the inference is stopped, or an empty list of rules for this input document is returned.
\end{enumerate}

\subsection{Data Flow using DOM parser}
When using the DOM parsing method, extraction of rules from a Schema document, mentioned in step 3 above, proceeds as follows.
\begin{enumerate}
	\item Document Object Model tree data structure is created from the input file by \emph{Xerces DOM parser}.
	\item Root node of the DOM tree is handed over to \code{DOMHandler} class.
	\item \code{DOMHandler} recursively passes the DOM tree by a depth-first algorithm and creates complete subtrees of rules (rule-trees) for each of the direct children of root node.
	\item Rule-trees are returned from \code{DOMHandler}.
	\item \code{DOMParser} traverses the returned rule-trees depth-first to create a list of final rules. Each of the rules now contains a full path, thanks to the way in which they were created.
\end{enumerate}

@@

Parsers with extended or custom functionality can be created using \code{XSDImportDOM} module as example (recomended).

>>>>

\subsection{Naming convention}
Note that there are several types of entities called ``element'' in the context of the described modules.
To avoid ambiguity, in this document we shall use notation \code{DOM.Element} 
for instances of \code{org.w3c.dom.Element} and notation \code{Element} 
for instances of\code{cz.cuni.mff.ksi.jinfer.base.objects.nodes.Element}.

@@

\begin{description}
	\item[CreateSentinel()] Creates an instance of \code{Element} class, which is always a leaf in the rule-tree. This is useful when there are cyclic definitions in an input Schema document, or an \code{Element} with this name was defined previously and it is unnecessary to build a rule subtree for it again (it is a reference in this case). More information about sentinels can be found in \cite[section 3.2]{archdoc}, or \cite[section 4]{twostepdoc}.
	\item[FinalizeElement()] Checks if \code{Element} is properly defined. Redefine it to \code{LAMBDA} when it was empty, or to \code{TOKEN} if it only contained a simple data type. This method allows for built-in data types of tags to be retained for export.
\end{description}

@@

Sax handler implements methods in response to the events generated by the underlying SAX parser API.
Similar to its counterpart \code{DOMHandler}, this class holds most on the logic for importing a Schema.
It works by keeping current tree branch, which is being parsed, on a stack. Adding current node to the parent on top of the stack as current tag closes.

\section{Data Flow}
Parsing of XSD begins when \code{IGGeneratorImpl} calls \code{XSDProcessor} with an input file.
The overall data flow while parsing a Schema document is simple, it can be summarized into following steps.
\begin{enumerate}
	\item \code{XSDProcessor} finds out the selected \code{XSDParser} from available service providers. This also indicates which module will be handling the actual parsing.
	\item \code{XSDProcessor} passes the input document to a selected module by calling \code{parse()} method on the selected \code{XSDParser}.
	\item Depending on the module, the corresponding API is used to extract IG rules from the input document.
	\item List of rules that were extracted from the document are returned to \code{XSDProcessor}.
	\item If no errors occured during this process, list of extracted rules is returned to \code{IGGeneratorImpl} for expansion (if needed). Otherwise, depending on the \emph{Stop on error} setting, the inference is stopped, or an empty list of rules for this input document is returned.
\end{enumerate}

\subsection{Data Flow using DOM parser}
When using the DOM parsing method, extraction of rules from a Schema document, mentioned in step 3 above, proceeds as follows.
\begin{enumerate}
	\item Document Object Model tree data structure is created from the input file by \emph{Xerces DOM parser}.
	\item Root node of the DOM tree is handed over to \code{DOMHandler} class.
	\item \code{DOMHandler} recursively passes the DOM tree by a depth-first algorithm and creates complete subtrees of rules (rule-trees) for each of the direct children of root node.
	\item Rule-trees are returned from \code{DOMHandler}.
	\item \code{DOMParser} traverses the returned rule-trees, depth-first, to create a list of final rules. Each of the rules now contains a full path, thanks to the way in which they were created.
\end{enumerate}

@@

Parsers with extended or custom functionality can be created using \code{XSDImportDOM} module as example (recommended).
